Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-12-03 Docs/IJES/journal.tex
add line numbers to the algorithms

Algorithm at Figure~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed.

Note that algorithm of Figure~\ref{Steps-Calculation-using-Intervals} is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
From lines $4$ to $9$, the algorithm finds the largest interval. Then, from line $10$ the largest interval is removed and the median is calculated in line $11$. After that, two new intervals are created, the left side (in line $14$) and the right side (in line $16$). At the end, the median is returned.

>>>>

Algorithm in Figure~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed.

Note that algorithm of Figure~\ref{Steps-Calculation-using-Intervals} is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
From lines $4$ to $9$, the algorithm finds the largest interval. Then, from line $10$ the largest interval is removed and the median is calculated in line $11$. After that, two new intervals are created, the left side (in line $14$) and the right side (in line $18$). At the end, the median is returned.
